\documentclass{article}
\usepackage{}
\usepackage{geometry}
\geometry{a4paper,scale=0.7}

\title{\textbf{My Road to Shanghai Jiaotong University}}
\author{\textbf{Kailing Wang:521030910356}}
\date{\textbf{2021.10.12}}

\begin{document}
	\maketitle

\paragraph
	\normalsize ``Fu Dan NB, I want to go to Jiao Da!'' in a video with hundreds of thousands views, one said. It's universally acknowledged that SJTU is one of the TOP3 universities in China. However, given the enormous number of people who sit in the college entrance exam every year, it's not easy at all to be admitted to SJTU. Fortunately, I became one of the few `succeeded' this year. For me, in addition to my luck, what sends me here is my ability and personality. To be exact: emotion control, self-discipline and will.

\paragraph
	\normalsize Looking back on all the way to SJTU, I find emotion control most important. It's significance lies in that it allows one to do everything else without the anxiety. This anxiety comes in all directions: people better than you can worry you, and the unknown future, especially during high school in my life experience, can be really disturbing from time to time. You are more likely to lose if you just let these emotion block you from stepping forward. Emotion control can clear out mental obstacles on your way to a higher level, and that's why I view it fundamental.

\paragraph
	\normalsize When you can control your emotions well, self-discipline leads you further. Let's think of emotion control as the roots, then self-discipline is the stem and leaf, without which you can never grow. Self-discipline is something that force you to cut down entertainment and improve your self through hard work. For example, during my three years of high school, while my classmates were enjoying TV series, reading some sort of youth literature and playing Honor of King even before final exams, I got done over a hundred exercise books, as well as thousand of exercise papers after class, which were sold over 100 yuan as recyclable waste after graduation. My self-discipline made me a better-learned student, and finally made me here.

\paragraph{}
	\normalsize If I say the former two `made' me here, then my will made me `here'. Will is just like the sun, which both give you the direction to grow and the energy to do so. Early in the Eight-provinces Joint Examination, SJTU is my dream school. I put all my work towards it ever since. Even when I knew my final grade could allow me to step into THU and PKU, I chose SJTU without second thought. Without my strong will, I might not be here at all. But I did. My will played the decisive role.

\paragraph{}
	\normalsize Thanks to these qualities, I am here. Emotion control sets the base, self-discipline builds the body and the will indicates the direction. But to become a tree that stands the storm, I have a longer way to go.
\end{document}