\documentclass{article}
\usepackage{ctex}
\usepackage{geometry}
\geometry{a4paper,scale=0.9}

\begin{document}

{

\Large
\noindent\textbf{Outline: Offline Does Fine}

\noindent\small\textbf{Kailing Wang 521030910356}
\\
	\large

	\noindent\textbf{Introduction}

		A.\qquad \textbf {Ground Fact:} Due to the seemingly everlasting COVID-19 pademic, online education is developing fast, and the trend is still going up. Indeed, online classes has its satisfying qualities.

		B.\qquad \textbf {Thesis:} However, as for the most important thing--teaching, offline class wins.

		C.\qquad \textbf {Preview of the main points:}

				\qquad\qquad The school environment increases willingness to learn.

				\qquad\qquad Students and teacher are physically closer.

				\qquad\qquad Offline is healthier.

	\noindent\textbf{Body:}

		A.\qquad The school environment increases willingness to learn.

			\qquad a. \textbf {Online:}

				\qquad\qquad 1)At home, feeling to relaxed(maybe even in bed).

				\qquad\qquad 2)Messy room, play things around, hard to focus.

				\qquad\qquad 3)Supervision needed.

			\qquad b. \textbf {Offline:}

				\qquad\qquad 1)At school, feeling like learning.

				\qquad\qquad 2)Tidy classroom, only books and study-related stuff are around.

				\qquad\qquad 3)Teachers watching all students. And teachers can...

		B.\qquad Students and teacher are physically closer.

			\qquad a. \textbf {Online:}

				\qquad\qquad 1)Hard to discuss. Mirophone control.

				\qquad\qquad 2)Explain mainly in words and PPT.

				\qquad\qquad 3)Distant. Cold, unreal feeling.

			\qquad b. \textbf {Offline:}

				\qquad\qquad 1)Face-to-face discuss.

				\qquad\qquad 2)Enable non-verbal explanation(action, real objets...).

				\qquad\qquad 3)Draw people closer. And also make people healthier...

		C.\qquad Offline is healthier.

			\qquad a. \textbf {Online:}

				\qquad\qquad 1)Staring at screen. All day on seat.(physical)

				\qquad\qquad 2)Lack companion.(psychological)

			\qquad b. \textbf {Offline:}

				\qquad\qquad 1)Eyes moving frequently. Activities between classes.

				\qquad\qquad 2)Being with fellows, teachers.

	\noindent\textbf{Conclusion}

		\qquad\qquad 1)Restatement. For a long time, offline study is better.

		\qquad\qquad 2)Funny ending(if possible).

}

\end{document}
